Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-03-14 src/tex/ms.tex
add information about Zenodo repo

\section*{Reproducibility}
All code required to reproduce our results, figures, and this article itself is available at \url{https://github.com/matiscke/originsoflife}.

>>>>

\section*{Reproducibility}
All code required to reproduce our results, figures, and this article itself is available at \url{https://github.com/matiscke/originsoflife}\rev{, and the repository has been archived on Zenodo at \url{https://zenodo.org/records/15022723}.}
